Follow-up Samples

### 2017-03-29 submission/manuscript_outline_20161024.tex

\textbf{Figure S2: ROC Curves of the Adenoma, Advanced Adenoma, and
Carcinoma Models.} A) Adenoma ROC curve: The light green shaded areas
represent the range of values of a 100 different 80/20 splits of the
test set data and the dark green line represents the model using 100\%
of the data set and what was used for subsequent classification. B) SRN
ROC curve: The light yellow shaded areas represent the range of values
of a 100 different 80/20 splits of the test set data and the dark yellow
line represents the model using 100\% of the data set and what was used
for subsequent classification. C) Carcinoma ROC curve: The light red
shaded areas represent the range of values of a 100 different 80/20
splits of the test set data and the dark red line represents the model
using 100\% of the data set and what was used for subsequent
classification.

\textbf{Figure S3: Summary of Important Variables for the Adenoma,
Advanced Adenoma, and Carcinoma Models.} A) MDA of the most important
variables in the adenoma model. The dark green point represents the mean
and the lighter green points are the value of each of the 100 different
runs. B) Summary of Important Variables in the SRN model. MDA of the
most important variables in the SRN model. The dark yellow point
represents the mean and the lighter yellow points are the value of each
of the 100 different runs. C) MDA of the most important variables in the
carcinoma model. The dark red point represents the mean and the lighter
red points are the value of each of the 100 different runs.

>>>>

\textbf{Figure S2: ROC Curves of the Adenoma, Advanced Adenoma, and
Carcinoma Models.} A) Adenoma ROC curve: The light green shaded areas
represent the range of values of a 100 different 80/20 splits of the
test set data and the dark green line represents the model using 100\%
of the data set and what was used for subsequent classification. B)
Advanced Adenoma ROC curve: The light yellow shaded areas represent the
range of values of a 100 different 80/20 splits of the test set data and
the dark yellow line represents the model using 100\% of the data set
and what was used for subsequent classification. C) Carcinoma ROC curve:
The light red shaded areas represent the range of values of a 100
different 80/20 splits of the test set data and the dark red line
represents the model using 100\% of the data set and what was used for
subsequent classification.

\textbf{Figure S3: Summary of Important Variables for the Adenoma,
Advanced Adenoma, and Carcinoma Models.} A) MDA of the most important
variables in the adenoma model. The dark green point represents the mean
and the lighter green points are the value of each of the 100 different
runs. B) Summary of Important Variables in the advanced adenoma model.
MDA of the most important variables in the SRN model. The dark yellow
point represents the mean and the lighter yellow points are the value of
each of the 100 different runs. C) MDA of the most important variables
in the carcinoma model. The dark red point represents the mean and the
lighter red points are the value of each of the 100 different runs.
